Discovery of Mg-depleted and K-enhanced Stars in \textit{LAMOST}

### 2018-02-02 article/ms.tex
Made changes in line with feedback and discussions with John and Amanda

Stellar absorption spectra act as a fossil record of the conditions where the stars form. Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with  depleted Mg and enhanced K abundances have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios. These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419. These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.

@@

\section{Introduction}
\label{sec:intro}
NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy. Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}.

The only known mechanism for Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude.

%Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$). The Mg depleted population identified previously was found to be contained with the G2 population.

A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that theK abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}. NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed. All 4 of NGC 2808's known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419. The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.

\todo{An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.}

@@

It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required. Using this information, core -- and shell --  burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars. Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified. The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material limits certainty in this case. However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.

@@

Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}. Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.

Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates. In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed. Section \ref{sec:conclusion} summarises the main results.}

@@

We identified potential Mg-K anti-correlated stars by searching for significant deviations in flux residuals. The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$). A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).

We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants in \lamost\ data release 2 (DR2). For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities. We identified candidates by requiring they match at least one of the following three quality filters:
\begin{enumerate}
\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$. Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
\item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
\end{enumerate}

@@

\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{Kvsmgmod.png}
    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The dotted line is arbitrary, and is present simply as a visual aide.}
    \label{KvsMg}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
    \label{KvsFe}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters. None of the stars appear to be associated with NGC 2419 or NGC 2808. \todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}. This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.}

The spread of metallicity shown in Figure \ref{mhist} further supports the sample being made up of field stars. The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
No stars are present at [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808. Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicites associated with NGC 2419 and NGC 2808.

\subsection{Abundances}
\label{sec:abundances}
Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra, these being similar to the [$\alpha$/Fe] abundances from \tc.

[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra suggest that at most a small depletion relative to the Mg-normal population in NGC 2419 may be present.

A similar relationship emerges when comparing with typical galactic numbers for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
Only the sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample are likely to have extremely high levels of [K/Fe].

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}. This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases. It is interesting that the Mg-poor population of NGC 2419 appears to fit this relation.

@@

The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although again it's possible a slight depletion is present. No variation with metallicity is observed for [$\alpha$/Fe].

@@

[Na/Fe] was also measured for the \lamost\ data. Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}. However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels. \todo{It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.}

The implications of the calculated abundances are intriguing. The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern.

The 112 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and exist at a range of metalicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

@@

This interpretation argues against any theoretical hyper-massive Population III star, no matter how contrived, being the polluter candidate. While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the cluster, it cannot account for the production of K throughout the life of the galaxy.

As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K. Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}. This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.

Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature along with (inconsistently) depleted Mg and enhanced Na throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star. The scenario might proceed as follows:

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through binary accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope. In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.

@@

\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}

More generally, the [K/Fe]-[Fe/H] anti-correlation observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters. However, this is not necessarily the only interpretation. For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason this would be the case.

\section{Conclusions}
\label{sec:conclusion}
Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra. These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects. The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.

Upon conducting an abundance analysis, it was found that despite searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of [K/Fe] relative to galactic levels. None of the candidates had calculated abundances of Mg or K consistent with the extreme populations of NGC 2419 or NGC 2808.

An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further observations of the candidates.

>>>>

Stellar absorption spectra act as a fossil record of the conditions where the stars form. Stars with unusual elemental abundances are of particular interest; these rare stars offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with  depleted Mg and enhanced K abundances have so far only been found in the two massive globular clusters NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that uncertain [Mg/Fe] but significantly enhanced [K/Fe] abundance ratios. These stars are present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419. These candidate stars should provide guidance for follow up surveys and modelling attempting to determine the origin of the Mg-K anti-correlation.

@@

\section{Introduction}
\label{sec:intro}
NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy. Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V with Mg \citep{mucciarelli2012,cohenkirby2012}.

A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that the K abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}. NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed. All 4 of NGC 2808's known Mg-depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419. The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.

One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude.

The other avenue for potentially reducing [Mg/Fe] is high temperature H-burning through Mg-Al chains. However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.

%Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$). The Mg-depleted population identified previously was found to be contained with the G2 population.

\todo{An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 $\times 10^6$ K (hereafter MK).}

@@

It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required. Using this information, core and shell burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars. Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified. The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty. However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.

@@

Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}. Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K, if their results can be confirmed in a fully 3D simulation. Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts to understand globular cluster formation and evolution.

Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena. In particular, the search should provide strong evidence for the uniqueness of the mysterious site of nucleosynthesis responsible for the pattern to globular clusters, or lack thereof. \todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates. In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed. Section \ref{sec:conclusion} summarises the main results.}

@@

We identified potential Mg-K anti-correlated stars by searching for significant deviations in flux residuals. The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$). A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model). Figure 1 shows the LAMOST spectra, along with the star's model from the \tc, for candidate J034458.82+592955.1.

We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants. For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities. We identified candidates by requiring they match at least one of the following three quality filters:
\begin{enumerate}
\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$. Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
\item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
\end{enumerate}

@@

\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{Kvsmgmod.png}
    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe]. The dotted line is arbitrary, and is present simply as a visual aide.}
    \label{KvsMg}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. Metalicities for NGC 2808 are taken as the average metalicity for the cluster from \citet{harris1996}, as individual metallicities for these stars were not available.}
    \label{KvsFe}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters. None of the stars appear to be associated with NGC 2419 or NGC 2808. \todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}. This separation is large for association with such a small, distant cluster and the star's metallicity of -0.24 dex and apparent magnitude make it even less likely to be a member.}

The spread of metallicity shown in Figure \ref{mhist} further supports the sample being made up of field stars. The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
No stars are present with [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808. Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicites associated with NGC 2419 and NGC 2808.

\subsection{Abundances}
\label{sec:abundances}
Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. As described in \ref{sec:method}, acceptably reliable abundances for Mg were unable to be obtained using the \lamost\ spectra. The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data. However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].

[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419, although the small sample of these stars for which we have high resolution spectra means we are unable to confidently generalise this to the entire sample.

A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}. This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases. It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation. \todo{make figure in python, add trend line}

@@

The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], as were the levels of [Mg/Fe] from the high resolution Magellan/MIKE spectra. Once again the inability to decouple [Mg/Fe] from $[\alpha$/Fe] means we are unable do draw firm conclusions about whether [Mg/Fe] is depleted relative to typical field stars, although the data we do have suggests not. No variation with metallicity is observed for [$\alpha$/Fe], including GCE effects relating of Type Ia supernovae enrichments.

@@

[Na/Fe] was also measured for the \lamost\ data. Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}. However, this behaviour is very likely due to the effect of interstellar dust. This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels. \todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, no relation between Na and K abundance is observed.}

The implications of the calculated abundances are intriguing. The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern. It is worth repeating however that the sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.

The 112 star candidate pool of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

@@

This interpretation argues against any theoretical hyper-massive Population III star, no matter how contrived, being the polluter candidate. While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the anti-correlation to the cluster, its isolation from the Milky Way, and its low metallicity of $\sim -2$, this solution cannot account for the production of K throughout the life of the galaxy.

As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K. Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}. This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.

Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature -- along with (inconsistently) depleted Mg and enhanced Na -- throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is a less massive star. The scenario might proceed as follows:

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through wind-based accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope. In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.

@@

\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}

Another issue facing the above scenario is that it requires a single gas cloud to form many generations of stars to be formed almost continously to be consistent with Figure \ref{KvsFe}. This is only known to occur in inside galaxies, which are massive enough and have sufficient gas to form multiple star forming regions. For smaller gas clouds, typically only one generation is formed before the remaining gas is lost through stellar winds. Although it is tempting to attempt to satisfy such concerns by allowing the stars to have formed some dwarf galaxy which then merged with the Milky Way, if the initial gas cloud increases so significantly in mass, then the difficulty of polluting such a cloud in the first place with such high levels of K increases proportionately.

More generally, the [K/Fe]-[Fe/H] anti-correlation observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters. However, this is not necessarily the only interpretation. For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.

\section{Conclusions}
\label{sec:conclusion}
Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra. These stars show every appearance of being field stars, and they do not have the hallmarks of being the product of NLTE effects. The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.
